Legends for supplementary material

### 2019-05-16 Manuscript/Supplementary/supplementary_legends.Rmd
added two supplementary tables and updated legends

>>>>

**Supplementary Table 6. Full list of aggregated performances for GM12878.** Performances were stratified by resolution, resampling technique, and predictor type, and then averaged across chromosomes.

**Supplementary Table 7. Full list of aggregated performances for K562.** Performances were stratified by resolution, resampling technique, and predictor type, and then averaged across chromosomes.
